---
title: "Tutorial 9"
author: "XXXX"
output:
  pdf_document:
    citation_package: natbib
    highlight: tango
    number_sections: yes
    toc: yes
    toc_depth: 2
  html_document:
    df_print: paged
    toc: yes
    toc_depth: '2'
bibliography: references.bib 
biblio-style: dinat
subtitle: Team name
header-includes:
- \usepackage{titling}
- \pretitle{\begin{center} 
  \includegraphics[width=5in,height=6in]{Images/sam-albury-oA7MMRxTVzo-unsplash.jpg}\LARGE\\}
- \posttitle{\end{center}}
- \usepackage{fontawesome}
- \usepackage[most]{tcolorbox}
- \usepackage{xcolor}
- \usepackage{sectsty}
- \sectionfont{\color{blue}}
- \usepackage{verbatim}
- \usepackage{fancyhdr}
- \pagestyle{fancy}
---

\clearpage

# Section 1: Murder statistics

```{r readingdata, eval = FALSE, message = FALSE}
library(lubridate)
library(tidyverse)
library(ggplot2)
library(kableExtra)

dataset <- read.csv("Data/crime_table.csv")
murder_data <- dataset %>% filter(Offence.Subgroup == "A11 Murder") %>%
  select(ï..Year, Offence.Subgroup, Incidents.Recorded, Rate.per.100.000.population) %>%
  rename(Year = ï..Year, Offence = Offence.Subgroup, Incidents = Incidents.Recorded, Rate = Rate.per.100.000.population)
```

This section is examing how the offence 'A11 Murder' has changed over time in Victoria from January 2010 to December 2019.

Table /@ref(tab:murdertab) below shows this summarised data set with the incidents and rate per 100,000 people recorded.

The data will be examined further to see if any trends emerge.


```{r murdertab, eval = FALSE, message = FALSE}
murder_data %>%
  kable(caption = "Murder statistics in Victoria") %>%
  kable_styling(bootstrap_options = c("striped", "bordered", "hover"))
```

This data is visualised in Figure /@ref(fig:murderplot).

It appears that there is a slight increase in murder over time with the lowest levels recored in the earliest years of the decade and increasing towards 2019.

This relationship could be the basis of a future regression analysis.


```{r murderplot, fig.cap = "Change in murder incidents over time", eval + FALSE, message = FALSE}
murder_data %>%
  ggplot(aes(x=Year, y = Incidents, group_by(Year))) +
  geom_point()
```


\clearpage

# Section 2


\clearpage

# Section 3


\clearpage

# Section 4


\clearpage

# Citation examples

[More styles for natbib here](https://www.overleaf.com/learn/latex/Natbib_bibliography_styles)


 @BC64 and this is another article about COVID @bai2020presumed and I can also cite R packages as follows @ggplot2
